Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs

### 2020-02-05 main.tex
Add highway figure
Updates from Overleaf

Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(\bu^*)$, at a polynomial rate. However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $\forall t, A(\theta(t))\in\cC_{[N],\delta}$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight. However, this gap can be bounded with additional assumptions:
\begin{theorem}[Sample complexity]
\label{thm:control-error}
Under some assumptions specified in the proof, which amounts to
\begin{enumerate}
	\item the reward function $R$ is lipschitz;
	\item a persistent excitation assumption;
	\item a stability condition in the form of an LMI;
\end{enumerate}
 we can bound the approximation error of \autoref{alg:full}:
\begin{equation*}
\hat{V}^r(\bu) \leq {V}^r(\bu) \leq V(\bu) \leq \hat{V}^r(\bu) + \Delta_\omega + \cO\left({\log N / N}\right)
\end{equation*}
where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to the perturbations $\omega(t)$, with knowledge of $A(\theta)$. % $\max_a \sum_n \min_\omega$
\end{theorem}

@@

@@

We first bound the model estimation error.
\begin{lemma}
Under sufficient excitations in the features 
\begin{align}
\label{eq:excitation}
\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,\nonumber\\ \underline{\phi}^2 \leq \lambda(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
\end{align}
then,
\[\|A(\theta) - A(\theta_{[N],\lambda})\|_2 = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
\end{lemma}
\begin{proof}
By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $\lambda_{\min}(G_{[N],\lambda,i,j}) \geq N\underline{\phi}^2 $

Hence, by \eqref{eq:confidence-ellipsoid} we have 
\begin{align*}
	\|\theta - \theta_{[N],\lambda}\|_{G_{[N],\lambda}} \geq \sqrt{N}\underline{\phi} \|\theta - \theta_{[N],\lambda}\|_{2} 
\end{align*}
and \eqref{eq:beta_n} gives

@@

And $A(\theta)$ belongs to a linear image of this ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
\begin{align*}
((A(\theta)&-A(\theta_{[N],\lambda}))^\transp (A(\theta) - A(\theta_{[N],\lambda})))_{i,j}\\
%&= (\phi_i(\theta-\theta_{[N],\lambda}))^\transp \phi_j(\theta-\theta_{[N],\lambda}) \\
&= (\theta-\theta_{[N],\lambda})^\transp\phi_{i}^{\transp}\phi_j(\theta-\theta_{[N],\lambda}) \\
&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{[N],\lambda}\|_{2}^2 = \cO\left( {\frac{\log N}{N}} \right) 
\end{align*}

>>>>

Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(\bu^*)$, at a polynomial rate. However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $\forall t, A(\theta(t))\in\cC_{[N],\delta}$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight. However, this gap can be bounded with additional assumptions:
\begin{theorem}[Sample complexity]
\label{thm:control-error}
Under some assumptions specified in the proof, which amounts to
\begin{enumerate}
	\item a regularity (lipschitz) assumption for the reward $R$;
	\item a persistent excitation (PE) assumption;
	\item a stability condition in the form of an LMI;
\end{enumerate}
 we can bound the approximation error of \autoref{alg:full}:
\begin{equation*}
\hat{V}^r(\bu) \leq {V}^r(\bu) \leq V(\bu) \leq \hat{V}^r(\bu) + \Delta_\omega + \cO\left({\log N / N}\right)
\end{equation*}
where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to instantaneous perturbations $\omega(t)$, with knowledge of $A(\theta)$. % $\max_a \sum_n \min_\omega$
\end{theorem}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{img/highway-small}
	\caption{The intersection crossing task.}
\end{figure}

@@

We first bound the model estimation error.
\begin{lemma}
If the features $\Phi_n$ are persistently exciting:
\begin{align}
\label{eq:excitation}
\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,\nonumber\\ \underline{\phi}^2 \leq \lambda_{\min}(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
\end{align}
then,
\[\|A(\theta) - A(\theta_{[N],\lambda})\|_2 = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
\end{lemma}
\begin{proof}
By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $$\lambda_{\min}(G_{[N],\lambda,i,j}) \geq (N-n_0)\underline{\phi}^2 + \sum_{n<n_0}\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}$$

Hence, by \eqref{eq:confidence-ellipsoid} we have 
\begin{align*}
	\|\theta - \theta_{[N],\lambda}\|_{G_{[N],\lambda}} \geq (\sqrt{N}\underline{\phi} + \cO(1))\|\theta - \theta_{[N],\lambda}\|_{2}
\end{align*}
and \eqref{eq:beta_n} gives

@@

And $A(\theta)$ belongs to a linear image of this $L^2$-ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
\begin{align*}
((A(\theta)&-A(\theta_{[N],\lambda}))^\transp (A(\theta) - A(\theta_{[N],\lambda})))_{i,j}\\
%&= (\phi_i(\theta-\theta_{[N],\lambda}))^\transp \phi_j(\theta-\theta_{[N],\lambda}) \\
&= (\theta-\theta_{[N],\lambda})^\transp\phi_{i}^{\transp}\phi_j(\theta-\theta_{[N],\lambda}) \\
&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{[N],\lambda}\|_{2}^2 = \cO\left( {\frac{\log N}{N}} \right) 
\end{align*}
